The \frb\ Campaign: A Multi-Telescope Burst Detection and Implications for the FRB Population

### 2017-04-12 repeater-vladata.tex
flux density scale issue discussed better

Figure \ref{fig:sgram} shows a dynamic spectrum for this burst with both VLA and Arecibo data. The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the Arecibo temporal grid after correcting for barycentric and dispersion measure offsets. We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from the top of the VLA and Arecibo bands, respectively. We used PRESTO \citep{2001PhDT.......123R} to calculate a barycentric time offset of 3.8~ms between the VLA and Arecibo data.

@@

**integrated flux is assuming 5 ms width!**

**confirm arecibo integrated flux and sensitivity**

Figure \ref{fig:multi} shows spectra built from integrated flux densities measured (or limited) during three burst with multi-telescope observing coverage. The burst on 17 Sep 2016 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$\ with integrated flux densities of 111 mJy and 14 mJy at 3 and 1.4~GHz, respectively. The VLA integration time of 5~ms underresolves the pulse and the true integrated flux density would be 280 mJy for an assumed pulse width of 2~ms.
% correct the followign for estimated integrated flux
Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.7$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<0.6$\ for a 2~ms burst and $5\sigma$ limit).

@@

To better understand the spectra, we used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency). We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}. The dynamic spectra were modeled with a broad Gaussian envelope (amplitude, center, width), a time delay according to the $\nu^2$\ dispersion law, and a square pulse of temporal width. We use a log likelihood function $\ln \mathcal{L}=(-1/2)\ \sum_i (S_i - S_{i, \rm{model}})^2/\sigma_s^2$, where $S_i$\ refers to the measured and modeled flux density in a single pixel of the dynamic spectrum and $\sigma_s\approx 70\ \mu$Jy is the measured off-burst noise per 5~ms integration and 4~MHz channel. A flat prior was used over all ranges with valid data with the requirement that the integrated signal must have a detection significance higher than 8$\sigma$. The 6-dimensional models were sampled with 100 chains taking 700 steps; we ignored the first 200 steps to properly sample the posterior distributions.

>>>>

Figure \ref{fig:sgram} shows a dynamic spectrum for this burst with both VLA and Arecibo data. The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the Arecibo temporal grid after correcting for barycentric and dispersion measure offsets. We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from the top of the VLA and Arecibo bands, respectively. We used PRESTO \citep{2001PhDT.......123R} to calculate a barycentric time offset of 3.8~ms between the VLA and Arecibo at the time of observation.

@@

**redo multispec figure and comparison of \alpha**

Figure \ref{fig:multi} shows spectra built from integrated flux densities measured (or limited) during three burst with multi-telescope observing coverage. The burst on 17 Sep 2016 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities of in 5~ms of 111 mJy and 14 mJy at 3 and 1.4~GHz, respectively. Here we assume a typical pulse width of 2~ms and measure VLA and Arecibo integrated flux densities of **xx and yy mJy** at 3 and 1.4~GHz, respectively.
Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.7$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<0.6$\ for a 2~ms burst and $5\sigma$ limit).

@@

We used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency). We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}. The dynamic spectra were modeled with a broad Gaussian envelope (amplitude, center, width), a time delay according to the $\nu^2$\ dispersion law, and a square pulse of temporal width. We use a log likelihood function $\ln \mathcal{L}=(-1/2)\ \sum_i (S_i - S_{i, \rm{model}})^2/\sigma_s^2$, where $S_i$\ refers to the measured and modeled flux density in a single pixel of the dynamic spectrum and $\sigma_s\approx 70\ \mu$Jy is the measured off-burst noise per 5~ms integration and 4~MHz channel. A flat prior was used over all ranges with valid data with the requirement that the integrated signal must have a detection significance higher than 8$\sigma$. The 6-dimensional models were sampled with 100 chains taking 700 steps; we ignored the first 200 steps to properly sample the posterior distributions.
